---
title: "dipr hexsticker"
output:
  html_document:
    df_print: paged
---


```{r setup}
library(hexSticker)
library(tidyverse)

```

https://github.com/GuangchuangYu/hexSticker 


## fonts & colours

```{r}

library(showtext)
## Loading Google fonts (http://www.google.com/fonts)
#font_add_google("Astronaut Jones", "astronautjones")
font_add_google("Raleway", "raleway")
font_add_google("Roboto Slab", "roboto_slab")

# BC Sans
#  https://www2.gov.bc.ca/gov/content/governments/services-for-government/policies-procedures/bc-visual-identity/bc-sans

## loading local font 
font_add("BCSans-Regular", 
         regular = "C:\\USERS\\USER\\APPDATA\\LOCAL\\MICROSOFT\\Windows\\Fonts\\BCSANS-REGULAR.OTF")

font_add("BCSans-Bold", 
         regular = "C:\\USERS\\USER\\APPDATA\\LOCAL\\MICROSOFT\\Windows\\Fonts\\BCSans-Bold.otf")


## Automatically use showtext to render text for future devices
showtext_auto()


```


### colours


```{r}

# BC Gov palette (of two colours)
# https://www2.gov.bc.ca/gov/content/governments/services-for-government/policies-procedures/bc-visual-identity/design-guidelines#palette-typography
BC_yellow <- "#e3a82b"  # R 227 G 168 B 43
BC_blue <- "#234075"    # R 35 G 64 B 117
# variants via coolors.co
BC_yellow2 <- "#F2D79E"
BC_yellow3 <- "#FFEECC"
BC_blue2 <- "#9BA8C0"  # R 155 G 168 B 192


# Night Sky palette
# https://colorswall.com/palette/2162/
ns_dark <- "#0c1445"    #rgb(12,20,69)  
ns_medium <- "#4c408e"    #rgb(76,64,142)
ns_light <- "#5c54a4"  #rgb(92,84,164)
ns_meddark <- "#38285c" #rgb(56,40,92)


```





## constellation (a pun)


Big Dipper x-y coordinates from [Creating Constellations on a Coordinate Plane](http://www.tsgc.utexas.edu/space_vision/constellations.pdf)

Apparent magnitude from ["Big Dipper" Wikipedia entry](https://en.wikipedia.org/wiki/Big_Dipper) and associated pages for individual stars



```{r}

dipper <- tribble(
  ~name, ~x, ~y, ~mag,
  "Alkaid or Benetnash", -18, 3, 1.85,
  "Mizar", -11, 4, 2.04,
  "Alioth", -6, 3, 1.76,
  "Megrez", 1, 1, 3.312,
  "Phecda", 3, -5, 2.44,
  "Merak", 13, -5, 2.37,
  "Dubhe", 15, 3, 1.79
)

# reverse magnitude 
#   note: magnitude is measured on log scale 
#   https://en.wikipedia.org/wiki/Apparent_magnitude

dipper <- dipper %>% 
  mutate(mag_rev = 1/log(mag))

dipper
```


some preliminary plots

```{r}

p_test <- ggplot(dipper, aes(x = x, y = y)) + 
  geom_point()
p_test

# add scale size an
p_test + 
  scale_size_area() +
  coord_equal()

```

with significant refinements

* turn point into a circle (with colour and fill)

* join the dots

```{r}

p <-
ggplot(dipper, aes(x = x, y = y, size = mag_rev)) + 
  # add line segments between points
  geom_path(size = 0.25, colour = BC_yellow2) +
  annotate("segment", 
           size = 0.25, colour = BC_yellow2,
           x = dipper$x[4], y = dipper$y[4],       # coordinates for Megrez
           xend = dipper$x[7], yend = dipper$y[7]) + # coordinates for Dubhe
  # points, size by area
  geom_point(shape = 21, colour = BC_yellow3, fill = BC_yellow) +
  scale_size(range = c(1, 2)) +
  # set equal length x and y 
  coord_equal() +
#  xlim(-18, 15) +
  ylim(-8, 8)

p

p <- p +
  theme_void() +
  theme(legend.position = "none")
p

ggplot2::ggsave("dipper_image.png", scale = 1)

```



```{r}

dipr_hex <- 
  sticker(p, package="dipr", 
          s_x=1, s_y=.75, s_width=1.4, s_height=1.4,
        h_fill=BC_blue, h_color=BC_yellow, h_size = 1.5,
        p_color = BC_blue2,
        p_size=32, 
        p_family = "BCSans-Bold")

plot(dipr_hex)

#ggplot2::ggsave("BIDA302_hex.png", width = 2, height = 2)

```



## security (literal)

<div>Icons made by <a href="https://www.flaticon.com/authors/smashicons" title="Smashicons">Smashicons</a> from <a href="https://www.flaticon.com/" title="Flaticon">www.flaticon.com</a></div>

https://www.flaticon.com/free-icon/safe_2488702?term=vault&page=1&position=1


```{r}

dipr_hex <- 
  sticker("vault.png", package="dipr", 
          s_x=1, s_y=.7, s_width=.4, s_height=.4,
        h_fill=BC_blue2, h_color=BC_blue, h_size = 1.5,
        p_color = BC_blue,
        p_size=30, 
        p_family = "BCSans-Bold")

plot(dipr_hex)

#ggplot2::ggsave("BIDA302_hex.png", width = 2, height = 2)

```



```{r}

dipr_hex <- 
  sticker("vault_BCyellow.png", package="dipr", 
          s_x=1, s_y=.7, s_width=.4, s_height=.4,
        h_fill=BC_blue, h_color=BC_yellow, h_size = 1.5,
        p_color = BC_blue2,
        p_size=32, 
        p_family = "BCSans-Bold")

plot(dipr_hex)

#ggplot2::ggsave("BIDA302_hex.png", width = 2, height = 2)

```


### dipper the bird (another pun)

icon source: https://www.allaboutbirds.org/guide/American_Dipper/overview


```{r}

dipr_hex <- 
  sticker("icon-dipper_blue.png", package="dipr", 
          s_x=1, s_y=.7, s_width=.4, s_height=.4,
        h_fill=BC_blue, h_color=BC_yellow, h_size = 1.5,
        p_color = BC_blue2,
        p_size=32, 
        p_family = "BCSans-Bold")

plot(dipr_hex)

#ggplot2::ggsave("BIDA302_hex.png", width = 2, height = 2)

```



```{r}

dipr_hex <- 
  sticker("icon-dipper_blue.png", package="dipr", 
          s_x=1, s_y=.7, s_width=.45, s_height=.45,
        h_fill=BC_blue, h_color=BC_yellow, h_size = 1.5,
        p_color = BC_yellow,
        p_size=32, 
        p_family = "BCSans-Bold")

plot(dipr_hex)

#ggplot2::ggsave("BIDA302_hex.png", width = 2, height = 2)

```

### dipper photos

_Cinclus mexicanus_

http://nwbirdblog.blogspot.com/2011/10/american-dipper.html


```{r}

#image colours
dip_1 <- "#b5b2b4"
dip_2 <- "#bcc3cd"
dip_3 <- "#675d51"

dipr_hex <- 
  sticker("img_nwbirdblog/_DSC0388[245][1600] (American Dipper).jpg", package="dipr", 
          s_x=1, s_y=.9, 
          s_width=1.25, s_height=1.25,
        h_fill=dip_2, h_color=BC_yellow, 
        h_size = 1.5, 
        p_color = BC_blue,
        p_size=32, 
        p_y=1.6,
        p_family = "BCSans-Bold")

plot(dipr_hex)

#ggplot2::ggsave("BIDA302_hex.png", width = 2, height = 2)

```

https://www.audubon.org/field-guide/bird/american-dipper

http://vireo.ansp.org/search.html?Form=Search&SEARCHBY=Common&KEYWORDS=american+dipper&RESULTS=100&Search2=Search

https://ornithologi.com/2018/02/14/american-dipper-cinclus-mexicanus-illustration-with-a-note-on-the-evolution-of-cinclidae/

**_flickr creative commons_**

https://flickr.com/photos/ericellingson/31414482320/

https://flickr.com/photos/amaizlish/39303297534/
39303297534_9987f76e5f_q



```{r}

#image colours
dip_1 <- "#4e4c44"
dip_2 <- "#3e3341"

dipr_hex <- 
  sticker("img/39303297534_59ff7ba50f_o.jpg", package="dipr", 
          s_x=1, s_y=.7, s_width=.45, s_height=.45,
        h_fill=dip_1, h_color=BC_yellow, h_size = 1.5,
        p_color = BC_yellow,
        p_size=32, 
        p_family = "BCSans-Bold")

plot(dipr_hex)

#ggplot2::ggsave("BIDA302_hex.png", width = 2, height = 2)

```

## References

https://kimnewzealand.github.io/2019/02/21/celestial-maps/

http://www.datasketch.es/may/
http://www.datasketch.es/may/code/nadieh/

